---
title: "Fernandez2024"
author: "Ignacio Ramos-Gutiérrez" #author of the Rmd!
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Data origin reference:
Data generated at Herbario Universidad de Sevilla, in a project granted for Andalusian Protected Areas (J. Arroyo, M. Arista).

Primary data compiler:
M. Pilar Fernández Díaz

Other data compilers: 

## Notes

-  Occurrence precision was categorized into 4 groups depending on the info in the voucher (1km radius, <5km; 5-10km, >10km).
- Occurrences with a radius >10km were disregarded (10932 data)
- Buffers were created for the rest of the precision values. If > 75% of the surface fell into 1 cell, it was selected.


## Packages

```{r, message=FALSE}
library(here)
library(tidyverse)
library(tidylog)
library(terra)

source(here::here("R/AFLIBER_functions.R"))
```


## Load dataset

```{r}
citationkey <- "Fernandez2024"
# dt_raw <- readr::read_csv(here(paste0("inst/",citationkey,"/raw/XXXXXX.csv")))
dt_raw <- readxl::read_excel(here(paste0("inst/",citationkey,"/raw/Tabla Andalucia 23-12-24 AFLIBER.xlsx"))) |> 
  filter(Prec != ">10")

utm10 <- terra::vect(here::here("data-raw/Iberian_Peninsula_10x10_Grid/Iberian_Peninsula_10x10_Grid.shp"))

```


## Modify dataset

```{r}
#modify variables

dt_spat <- dt_raw |> 
    mutate(X_30S = as.numeric(X_30S),
           Y_30S = as.numeric(Y_30S)) |> 
  mutate(radius = case_when(Prec == "<5" ~ 5,
                            Prec == "1" ~ 1,
                            Prec == "5-10" ~ 10)) |> 
  terra::vect(geom = c("X_30S", "Y_30S")) 

get_major_grid <- function(point, buffer.radius){
  buffer <- terra::buffer(point, width = buffer.radius*1000) |> 
    simplifyGeom()
  crop <- terra::crop( utm10, buffer)
  crop$area <- suppressWarnings(terra::expanse(crop)/terra::expanse(buffer))
  if(any(crop$area>0.75)){
    return(crop$MGRS_10km[which(crop$area>0.75)])
  }else{
    return(NA)
  }
}


vals <- vector(length = length(dt_spat$ID))
for(i in 1:length(dt_spat$ID)){
 RIRG::progressbar(i, length(vals), units = "mins")
vals[i] <- get_major_grid(dt_spat[i,], dt_spat$radius[i])
}


dt_modif <- dt_raw |> 
  mutate(Taxon = ifelse(INFRANK == "subsp.", 
                        paste0(GENERO, " ", ESPECIE, " ", INFRA),
                        paste0(GENERO, " ", ESPECIE))) |> 
  mutate(UTM1x1 = NA,
         UTM10x10 = vals,
         References = "FlorAnd: Flora de Andalucía online. https://servicio.us.es/florand") |> 
  


    select(Taxon,
           UTM10x10, 
           UTM1x1, 
           References)


```


## Prepare dataset

```{r}

dt_modif$id <- 1:nrow(dt_modif)
# 
# #check allowed values
# check_taxa(dt_modif)  #see incorrect taxa
# check_cells(dt_modif)  #see incorrect cells

dt_check_vals <- dt_modif |> 
clean_values()


# Create dataset to compile
dt_include<- dt_check_vals |> 
  distinct(Taxon,
           UTM10x10, 
           UTM1x1, 
           References,
           id)

dt_save <- dt_modif |> 
  filter(!id %in% dt_include$id)

```
```{r}
readr::write_csv(select(dt_include, -matches("id") ),
                 here(paste0("inst/",citationkey,"/data/", citationkey,".csv")))

readr::write_csv(select(dt_save, -matches("id") ),
                 here(paste0("inst/",citationkey,"/data/", citationkey,"_notused.csv")))



```



## Session info

```{r}
sessioninfo::session_info()
```

